Learning constraints in tabular data

### 2016-05-20 Paper/ECAI/tabular.tex
fixed the algorithm

Our proposed methodology contains the following steps:
\begin{enumerate}
\item Extract headerless tables from tabular data
\item Partition the tables into maximally contiguous, type-consistent \textit{superblocks}
\item Generate for each constraint all valid argument assignments:
\begin{enumerate}
\item For each constraint $c$, generate all atoms $c(B_1, \ldots ,B_n)$ where each $B_i$ is a maximal \textit{superblock} and the $B_i$ are compatible with the signature.
\item For each generated atom $c(B_1, \ldots ,B_n)$, find all valid $c(B'_1, \ldots, B'_n)$ such that $\forall i, B'_i \sqsubseteq B_i$ and the signature and definition of $c(B'_1, \ldots, B'_n)$ is satisfied.
\end{enumerate}
\end{enumerate}

@@

\begin{algorithm}[t]
  \begin{algorithmic}
    \footnotesize
    \State \textbf{Input:} $\groups$ -- groups, $s$ -- constraint template
    \State \textbf{Output:} $C$ -- learned constraints
    \Procedure{LearnConstraints}{$\groups$, $s$}
    \State $C \gets \emptyset$ %\Comment{The set of constraints}
    \State $n \gets$ number of arguments of template $s$
    \State $A \gets \generategroups(s, \groups)$
    \ForAll{$(B_1, \dots, B_n) \in A$}
      \ForAll{$(B_1', \dots, B_n') \in \findassignment(s, (B_1, \dots, B_n))$}
        \State $C \gets C \cup \{ s(B_1', \dots, B_n') \}$
      \EndFor
    \EndFor
\Return $C$
\EndProcedure
\end{algorithmic}
\caption{Learn tabular constraints}
\label{algo:tcl}
\end{algorithm}

@@

\subsubsection{Constraints over satisfying subgroups} \label{sec:algo:subgr}
In the previous step, $\generategroups(\textit{t,{\cal G},C})$ generates tuples of candidate groups $(G_1, ..., G_n)$ for the constraint template $t$ with $n$ arguments. In this step, $\findassignment(t, (G_1, \dots, G_n))$, the goal is to enumerate the subgroups $(G'_1, ..., G'_n), \forall i, G'_i \subseteq G_i$ that satisfy both the signature and the definition of the constraint template $t$. The main difference with the previous step is that the group generation reasons about the \textit{properties} of the groups (type, size, length, ...), while this step reasons about the actual \textit{content} of the vectors in the groups, that is, the data.

@@

>>>>

Our proposed methodology contains the following steps:
\begin{enumerate}
\item Extract headerless tables from tabular data
\item Partition the tables into maximally contiguous, type-consistent \textit{superblocks}
\item Generate for each constraint all valid argument assignments:
\begin{enumerate}
\item For each constraint $c$, generate all atoms $c(B_1, \ldots ,B_n)$ where each $B_i$ is a maximal \textit{superblock} and the $B_i$ are compatible with the signature.
\item For each generated atom $c(B_1, \ldots ,B_n)$, find all valid $c(B'_1, \ldots, B'_n)$ such that for all $i$ holds $B'_i \sqsubseteq B_i$ and the signature and definition of $c(B'_1, \ldots, B'_n)$ are satisfied.
\end{enumerate}
\end{enumerate}

@@

\begin{algorithm}[t]
  \begin{algorithmic}
    \footnotesize
    \State \textbf{Input:} $\groups$ -- groups, $s$ -- constraint template
    \State \textbf{Output:} $C$ -- learned constraints
    \Procedure{LearnConstraints}{$\groups$, $s$}
    \State $C \gets \emptyset$ %\Comment{The set of constraints}
    \State $n \gets$ number of arguments of template $s$
    \State $A \gets \generategroups(s, \groups)$
    \ForAll{$(B_1, \dots, B_n) \in A$}
    \ForAll{${(B_1',\dots,B_n')\in}~\findassignment(s, (B_1,\dots,B_n))$}
        \State $C \gets C \cup \{ s(B_1', \dots, B_n') \}$
      \EndFor
    \EndFor
\Return $C$
\EndProcedure
\end{algorithmic}
\caption{Learn tabular constraints}
\label{algo:tcl}
\end{algorithm}

@@

\subsubsection{Constraints over satisfying subgroups} \label{sec:algo:subgr}
In the previous step, $\generategroups(\textit{t,{\cal G},C})$ generates tuples of candidate groups $(G_1, ..., G_n)$ for the constraint template $t$ with $n$ arguments. In this step, $\findassignment(t, (G_1, \dots, G_n))$, the goal is to enumerate the subgroups $(G'_1, ..., G'_n)$ (for all $i$, $G'_i \subseteq G_i$) that satisfy both the signature and the definition of the constraint template $t$. The main difference with the previous step is that the group generation reasons about the \textit{properties} of the groups (type, size, length, ...), while this step reasons about the actual \textit{content} of the vectors in the groups, that is, the data.

@@

\sergey{there should be a discussion on what to do if multiple constraints satisfy the data and propose predictions, just a sketch here for now}
If multiple constraints satisfy the data and allow autocompletion, then there is a number of ways to handle it. Firstly, autocompletion can be disabled. Secondly, the most specific constrain can be applied. If they are not compatible in the generality sense, one needs to introduce an autocompletion order, which would resolve the problem by picking only one constraint to suggest the values.
